Viscous Transport in Eroding Porous Media

### 2019-07-15 docs/transport/erosion_transport.tex
editing in transport paper

We also do not use any fast summation methods to apply the Barycentric
quadrature rule.  Since this quadrature rule is applied at every GMRES
iteration, it is imperative that we only apply the Barycentric
quadrature at target points where they are required.  As a rule of
thumb, the trapezoid rule due to $\gamma_k$ is accurate if
\begin{align}
  \label{eqn:TrapCutoff}
  d(\xx,\gamma_k) = \inf_{\yy \in \gamma_k} \|\xx - \yy\| > 
    5 \frac{L_k}{N_\iin}.
\end{align}
To avoid checking if all target point $\xx$
satisfy~\eqref{eqn:TrapCutoff}, we make use of the {\thL} variables.
First, given the two eroding bodies $\gamma_i$ and $\gamma_j$ with
lengths $L_i$ and $L_j$, and centers $\cc_i$ and $\cc_j$, we first check
if
\begin{align}
  \label{eqn:BodyCutoff}
  \|\cc_i - \cc_j\| < \frac{L_i}{2\pi} + \frac{L_j}{2\pi} + 
    \alpha_\iin \left(\frac{L_i}{N_\iin} + \frac{L_j}{N_\iin} \right),
\end{align}
where $\alpha_\iin \geq 1$ is a free parameter that needs to be chosen.
In this manner, rather than using an expensive all-to-all algorithm to
compute the distance between all pairs of discretization points, we
compute the distance between pairs of circles.  This criteria allows us
to quickly determine bodies that contain discretization points where the
Barycentric quadrature rule may need to be applied, and the parameter
$\alpha_\iin$ is accounts for the fact that the bodies are being
approximated with circles.  Assuming that the two bodies $\gamma_i$ and
$\gamma_j$ satisfy condition~\eqref{eqn:BodyCutoff}, for each point $\xx
\in \gamma_j$, we check if
{\color{red}
\begin{align}
  \label{eqn:PointsBodyCutoff}
  \|\xx - \cc_i\| < \frac{L_i}{2\pi} + \frac{L_j}{2\pi}
+ \alpha_\iin \left(\frac{L_i}{N_\iin} + \frac{L_j}{N_\iin} \right).
\end{align}
}
\todo[inline]{This doesn't seem right.  $\xx$ is already on the boundary
of the jth body, so $L_j$ should not be part of the criteria.  Should be
something more like equation (44).}
To determine if points on $\gamma_i$ are too close to the outer wall, we
use the fact that the outer wall is bounded in $[-3,3] \times [-1,1]$,
and that the bodies are all contained in $[-1,1] \times [-1,1]$.  We
first check if
\begin{align}
  \left\|\cc_i - \left[
    \begin{array}{c}
      x_{\cc_i } \\ \pm 1
    \end{array}
    \right]
  \right\| < \frac{L_i}{2 \pi} + \alpha_\out \frac{L_\out}{N_\out}
\end{align}
where $x_{\cc_i } $ is the x coordinate of $\cc_i$. If body $\gamma_i$
satisfies this condition, for each point $\xx=(x,y) \in \gamma_i$, we
apply the Barycentric rule to points that satisfy
\begin{align}
  \label{eqn:PointsWallCutoff}
  |y \pm 1| < \frac{L_i}{2 \pi} +\alpha_\out \frac{L_\out}{N_\out}.
\end{align}

@@

Since we use a Barycentric quadrature rule to approximate the velocity
of tracers and apply the fourth order Runge Kutta method to find the new
locations of tracers in each step, the tracers can be very close to but
not penetrate the bodies.  Those body-closed tracers are moving
perfectly so we are able to observe the details of the interaction of
bodies and fluid.  Although the direction of flow is from left to right,
the tracers will not only travel horizontally but also vertically.  In
the last three frames of Fig.~\ref{fig:Eroding20tracer}, some tracers
climb up from right to left around the body.  There are zoom windows of
the climbing tracers trajectories in Fig.~\ref{fig:Eroding20zoom} and
they are taken from the last three frames of
Fig.~\ref{fig:Eroding20tracer} with more tracers.  In
Fig.~\ref{fig:Eroding20zoom} the tracers around the center body first go
from the channel below the body, climb up to the left, then go to the
right and join another tracers in the channel above the body. 
}
\begin{figure}[H]
\begin{center}
\includegraphics[width = 0.32\textwidth]{./figs/tracer_20b210_zoom}
\includegraphics[width = 0.32\textwidth]{./figs/tracer_20b240_zoom}
\includegraphics[width = 0.32\textwidth]{./figs/tracer_20b270_zoom}
\caption{\label{fig:Eroding20zoom}The zoom windows in the last three
  frames of Figure~\ref{fig:Eroding20tracer}. The trajectories of
  tracers around the bodies. Since we use a Barycentric quadrature rule
  and the fourth order Runge Kutta method, the tracers can be very close
  to but not penetrate the bodies.}
\end{center}
\end{figure}
{\color{red}
In Fig.~\ref{fig:Eroding20area} we
measure the area occupied by bodies 
during the eroding. In the beginning, 62.32\% of area of $[-1,1] \times
[-1,1]$ is occupied by 20 bodies. Then the eroding speed is increasing
when more and more bodies are vanished in the fluid and 
the maximum eroding speed happens when 7.57\% of area of $[-1,1] \times
[-1,1]$ is occupied by 8 bodies. After that the speed drops rapidly to 0 when
all the bodies are vanished completely.

We record the flow rate $U$ quantifily in log scale
during the eroding in Fig.~\ref{fig:Eroding20flowrate}. 
Since we simulate the erosion by applying fixed pressure drop 
the flow rate $U$ is small when there are many bodies in the fluid and 
when the area occupied by bodies is getting smaller $U$ is getting larger.
When all the bodies have vanished completely the flow rate $U$ is equal to 1.
In Fig.~\ref{fig:Eroding20flowrate}, the flow rate increases exponentially 
with growth rate close to $\ln10^4$.

@@

\begin{figure}[H]
\begin{subfigure}[b]{0.5\textwidth}
\includegraphics*[width =\linewidth]{./figs/porosity20dense}
\caption{}
\end{subfigure}%
\begin{subfigure}[b]{0.5\textwidth}
\includegraphics*[width =\linewidth]{./figs/erodingspeed20dense}
\caption{}
\end{subfigure}
\caption{\label{fig:Eroding20area}  The area fraction of 20 nearly
  touching eroding bodies and the eroding speed verse time. }
\end{figure}

@@

\begin{figure}[H]
%\begin{subfigure}[b]{0.5\textwidth}
\center
\includegraphics*[width =0.5\linewidth]{./figs/flow_rate20dense}
%\caption{}
%\end{subfigure}%
%\begin{subfigure}[b]{0.5\textwidth}
%\includegraphics*[width =\linewidth]{./figs/flow_rate20dense}
%\caption{}
%\end{subfigure}
\caption{\label{fig:Eroding20flowrate}  The incoming flow rate of $U$ in log scale verse time. 
Under fixed pressure drop condition, $U$ will be small initially,
increase when bodies are eroding, and grow exponentially 
to 1 when there is no body in the fluid. }
\end{figure}

>>>>

We also do not use any fast summation methods to apply the Barycentric
quadrature rule.  Since this quadrature rule is applied at every GMRES
iteration, it is imperative that we only apply the Barycentric
quadrature at target points where they are required.  As a rule of
thumb, the trapezoid rule due to $\gamma_k$ is accurate if
\begin{align}
  \label{eqn:TrapCutoff}
  d(\xx,\gamma_k) = \inf_{\yy \in \gamma_k} \|\xx - \yy\| > 
    5 \frac{L_k}{N_\iin}.
\end{align}
To avoid checking if all target point $\xx$
satisfy~\eqref{eqn:TrapCutoff}, we make use of the {\thL} variables.
First, given the two eroding bodies $\gamma_i$ and $\gamma_j$ with
lengths $L_i$ and $L_j$, and centers $\cc_i$ and $\cc_j$, we first check
if
\begin{align}
  \label{eqn:BodyCutoff}
  \|\cc_i - \cc_j\| < \frac{L_i}{2\pi} + \frac{L_j}{2\pi} + 
    \alpha_\iin \left(\frac{L_i}{N_\iin} + \frac{L_j}{N_\iin} \right),
\end{align}
where $\alpha_\iin \geq 1$ is a free parameter that needs to be chosen.
In this manner, rather than using an expensive all-to-all algorithm to
compute the distance between all pairs of discretization points, we
compute the distance between pairs of circles.  This criteria allows us
to quickly determine bodies that contain discretization points where the
Barycentric quadrature rule may need to be applied, and the parameter
$\alpha_\iin$ is accounts for the fact that the bodies are being
approximated with circles.  Assuming that the two bodies $\gamma_i$ and
$\gamma_j$ satisfy condition~\eqref{eqn:BodyCutoff}, for each point $\xx
\in \gamma_j$, we check if
{\color{red}
\begin{align}
  \label{eqn:PointsBodyCutoff}
  \|\xx - \cc_i\| < \frac{L_i}{2\pi}
+ \alpha_\iin \left(\frac{L_i}{N_\iin} \right).
\end{align}
}
\todo[inline]{This doesn't seem right.  $\xx$ is already on the boundary
of the jth body, so $L_j$ should not be part of the criteria.  Should be
something more like equation (44).}
To determine if points on $\gamma_i$ are too close to the outer wall, we
use the fact that the outer wall is bounded in $[-3,3] \times [-1,1]$,
and that the bodies are all contained in $[-1,1] \times [-1,1]$.  We
first check if
\begin{align}
  \left\|\cc_i - \left[
    \begin{array}{c}
      x_{\cc_i } \\ \pm 1
    \end{array}
    \right]
  \right\| < \frac{L_i}{2 \pi} + \alpha_\out \frac{L_\out}{N_\out}
\end{align}
where $x_{\cc_i } $ is the x coordinate of $\cc_i$. If body $\gamma_i$
satisfies this condition, for each point $\xx=(x,y) \in \gamma_i$, we
apply the Barycentric rule to points that satisfy
\begin{align}
  \label{eqn:PointsWallCutoff}
  |y \pm 1| < \frac{L_i}{2 \pi} +\alpha_\out \frac{L_\out}{N_\out}.
\end{align}

@@

Since we use a Barycentric quadrature rule to approximate the velocity
of tracers and apply the fourth order Runge Kutta method to find the new
locations of tracers in each step, the tracers can be very close to but
not penetrate the bodies.  Those body-closed tracers are moving
perfectly so we are able to observe the details of the interaction of
bodies and fluid.  Although the direction of flow is from left to right,
the tracers will not only travel horizontally but also vertically.  In
the last three frames of Fig.~\ref{fig:Eroding20tracer}, some tracers
climb up from right to left around the body.  There are zoom windows of
the climbing tracers trajectories in Fig.~\ref{fig:Eroding20zoom} and
they are taken from the last three frames of
Fig.~\ref{fig:Eroding20tracer} with more tracers.  In
Fig.~\ref{fig:Eroding20zoom} the tracers around the center body first go
from the channel below the body, climb up to the left, then go to the
right and join another tracers in the channel above the body. 
}
\begin{figure}[H]
\begin{center}
\includegraphics[width = 0.32\textwidth]{./figs/tracer_20b210_zoom}
\includegraphics[width = 0.32\textwidth]{./figs/tracer_20b240_zoom}
\includegraphics[width = 0.32\textwidth]{./figs/tracer_20b270_zoom}
\caption{\label{fig:Eroding20zoom}The zoom windows in the last three
  frames of Figure~\ref{fig:Eroding20tracer}. The trajectories of
  tracers around the bodies. Since we use a Barycentric quadrature rule
  and the fourth order Runge Kutta method, the tracers can be very close
  to but not penetrate the bodies.}
\end{center}
\end{figure}
{\color{red}
In Fig.~\ref{fig:Eroding20area} (a) we
measure the area occupied by bodies 
during the eroding. In the beginning, 62.32\% of area of $[-1,1] \times
[-1,1]$ is occupied by 20 bodies. Then the eroding speed is increasing
when more and more bodies are vanished in the fluid and 
the maximum eroding speed happens when 7.57\% of area of $[-1,1] \times
[-1,1]$ is occupied by 8 bodies. After that the speed drops rapidly to 0 when
all the bodies are vanished completely.

We record the flow rate $U$ quantifily in log scale
during the eroding in Fig.~\ref{fig:Eroding20area} (b). 
Since we simulate the erosion by applying fixed pressure drop 
the flow rate $U$ is small when there are many bodies in the fluid and 
when the area occupied by bodies is getting smaller $U$ is getting larger.
When all the bodies have vanished completely the flow rate $U$ is equal to 1.
In Fig.~\ref{fig:Eroding20flowrate}, the flow rate increases exponentially 
with growth rate close to $\ln10^4$.

@@

\begin{figure}[H]
\begin{subfigure}[b]{0.5\textwidth}
\includegraphics*[width =\linewidth]{./figs/porosity20dense}
\caption{}
\end{subfigure}%
\begin{subfigure}[b]{0.5\textwidth}
\includegraphics*[width =\linewidth]{./figs/flow_rate20dense}
\caption{}
\end{subfigure}
\caption{\label{fig:Eroding20area}  (a) The area fraction of 20 nearly
  touching eroding bodies and the eroding speed versus time. 
(b) The incoming flow rate of $U$ in log scale versus time. 
Under fixed pressure drop condition, $U$ will be small initially,
increase when bodies are eroding, and grow exponentially 
to 1 when there is no body in the fluid. }
\end{figure}

@@
